---
title       : Learn about Chocolate!
subtitle    : Chocolate consumption and production
author      : Marina.K
job         : Individual leraner
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive, ggplot2]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- &radio

## Answer the Quiz!

Which country has largest chocolate consumption?

1. UK
2. France
3. _Germany_
4. USA

*** .hint
Beer and wienerwurst!

*** .explanation
Aren't you surprised?:)

---

## Chocolate Consumption by Country

Top 3 countries are in Europe.

```{r echo=FALSE, results='asis'}
require(rCharts)
Choco <- read.csv("hw1_data.csv", header = T)
n1 <- barplot(Choco$Consumption, names.arg = Choco$Country, xlab = "Country name", ylab = "Consumption of Chocolate")
```

--- &radio

## Answer the Quiz!

Which is the following is the biggest factor of chocolate evaluation?

1. Size of bean
2. _Percentage of cocoa_ 
3. Producer
4. No idea

*** .hint
Bitter is better.

*** .explanation
I don't think so, but fact said like that.

---
## Relationship between Percentage of cacao and its Evaluations
Please choose "Country", "Bean type" and "Cocoa percentage".
Note: If you can't see plot because of your operating environment, you can use it in a browser here[].
```{r echo=FALSE, results='asis'}
library(shiny)
library(ggplot2)
library(dplyr)
library(webshot)

cacao1 <- read.csv("flavors_of_cacao.csv", stringsAsFactors = FALSE)
ui <- fluidPage(
    titlePanel("Relationship between Percentage of coco & its Evaluation"),
    sidebarLayout(
        sidebarPanel(
            sliderInput("cocoInput", "CocoaPercent", 0, 1, c(0.4, 0.8)),
            radioButtons("typeInput", "BeanType",
                         choices = c("Blend", "Fresh"),
                         selected = "Fresh"),
            selectInput("countryInput", "Country",
                        choices = c("Germany", "France", "Japan"))
        ),
        mainPanel(
            plotOutput("plot1"),
            br(), br(),
            tableOutput("results")
        )
    )
)

server <- function(input, output) {
    output$plot1 <- renderPlot({
        filtered <-
            cacao1 %>%
            filter(CocoaPercent >= input$cocoInput[1],
                   CocoaPercent <= input$cocoInput[2],
                   BeanType == input$typeInput,
                   Country == input$countryInput
            )
        ggplot(filtered, aes(CocoaPercent)) +
            geom_histogram()
        ggplotly(G)
    })
}

shinyApp(ui = ui, server = server)
```
publish_github(Marina-Anna,PracticalMachineLearningCourseProject)